Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2021-02-21 NEUROC/sec7-conclusion.tex
sec7增加了Future Work和response_letter-Rev2_version1

\section*{Acknowledgements}

>>>>

% start, added by wangyunpan, 2021-2-21
In the future, we will focus on but not limited to the following directions:
%
\begin{enumerate}
    \item \emph{Performance bottlenecks in training/inference with multi-GPUs or distributed environments.}
    %
    For massive data in the real world, multi-GPUs and distributed training/inference are often the more common methods\cite{zhang2020_analysis_neugraph, zhu2019_aligraph}.
    %
    These methods will inevitably introduce overheads such as communication between GPUs (inter-machines). 
    %
    How these overheads affect performance bottlenecks is worthy to focus on.
    %
    \item \emph{Impacts of different programming models on performance bottlenecks.}
    %
    Our work is based on the mainstream programming model---messaging framework.
    %
    However, some GNNs systems also proposed some new programming models.
    %
    For example, NeuGraph\cite{zhang2020_analysis_neugraph} proposed the SAGA framework, 
    which includes four stages: Scatter, ApplyEdge, Gather, and ApplyVertex;
    %
    EuGN\cite{he2019_EnGN} provides an edge-centric programming model.
    %
    Whether different programming models will lead to changes in performance bottlenecks is worth discussing.
    %
    \item \emph{Impacts of spatial-temporal graph on performance bottlenecks.}
    %
    Spatial-temporal graphs appear in a variety of applications such as traffic speed forecasting\cite{li2018_DCRNN}, 
    driver maneuver anticipation\cite{jain2016_SRNN}, and human action recognition\cite{yan2018_STGCN}.
    %
    Learning hidden patterns from spatial-temporal graphs becomes increasingly important.
    %
    Many GNNs are also proposed\cite{li2018_DCRNN, jain2016_SRNN, yan2018_STGCN, seo2018_SSGCN, yu2018_STGCN}.
    %
    Whether spatial-temporal graphs will affect performance is worthy of our attention.
    %
\end{enumerate}
% end, added by wangyunpan, 2021-2-21
\section*{Acknowledgements}
